Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-09-01 Manuscript.Rmd
Fixed some captions

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey & Joseph T. McGuire"
output:
  html_document: default
  word_document: default
  pdf_document: default
bibliography: mPFC_paper.bib
---

@@

  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. This description will allow researchers to generate more precise topographic targets for future studies of decision making. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2013). We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning. The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects. Finally, we show some interesting properties of SP related to the stability of brain networks.

@@

```{r Meta-analysis ROIs, out.width="60%", fig.align = "center", fig.cap= "**Figure 1.** Template atlas from [-@Glasser2013] (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom). Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
include_graphics("./Images/ROIS.png")
```

@@

```{r Template partition, out.width="50%", fig.align = "center"}
# Load data
setwd('./Summary/')
temp <- list.files()
subjList <- sapply(temp, substring, first=1, last=6)
Summaries <- lapply(temp, read.csv)
nSubj <- length(Summaries)

include_graphics("./Images/template.png")
```

>>>>

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey & Joseph T. McGuire"
output:
  pdf_document: default
  word_document: default
  html_document: default
bibliography: mPFC_paper.bib
---

@@

  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. This description will allow researchers to generate more precise topographic targets for future studies of decision making. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2016). We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning. The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects. Finally, we show some interesting properties of SP related to the stability of brain networks.

@@

```{r Meta-analysis ROIs, out.width="60%", fig.align = "center", fig.cap= "Figure 1. Template atlas from Glasser et al. [-@Glasser2016] (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom). Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
include_graphics("./Images/ROIS2.png")
```

@@

```{r Template partition, out.width="60%", fig.align = "center", fig.cap = "Figure 2. Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
# Load data
setwd('./Summary/')
temp <- list.files()
subjList <- sapply(temp, substring, first=1, last=6)
Summaries <- lapply(temp, read.csv)
nSubj <- length(Summaries)

# fig caption
# "Figure 2. Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."

#include_graphics(c("./Images/newPattern.png", "./Images/newPattern_binary.png"))
include_graphics("./Images/newPattern_both.png")
```
